---
title: "IR Center Project"
author: "Nicholas Kaufman"
date: "2025-05-14"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, root.dir = "Users/nickkaufman/downloads")
library(readxl)
library(binom)
library(ggplot2)
library(devtools)
library(fANCOVA)
library(plotly)
library(dplyr)
library(tidyr)
library(corrplot)
library(lubridate)
library(patchwork)
library(effectsize)
library(Matrix)
library(mgcv)
library(ggpubr)
library(gratia) 
```

```{r}
Data <- read_excel("Mentoring Efficiency.xlsx")
col_types = c("text", "text", "date", 
"numeric", "numeric", "skip", "skip", 
"skip")

colnames(Data) <- c("Site", "Patient_Last_Name", "Procedure_Date", 
"Fluoroscopy_Time", "Radiation_Dose")

Data <- Data %>%
  mutate(Site = ifelse(Site == "St. Louis", "St.Louis", Site))

Data <- Data %>% na.omit(Data)

 ata <- Data[-c(106, 162, 176, 1287), ]
 Data <- Data[order(Data$Site, Data$Procedure_Date), ]
 Data$Month <- format(Data$Procedure_Date, "%B %Y")
 
Data <- Data %>%
  mutate(Month_Date = floor_date(Procedure_Date, unit = "month"),
         Month = format(Month_Date, "%B %Y")) 
Data <- Data %>%
  mutate(Site = factor(Site),
         Month = factor(Month, levels = unique(Month[order(Month_Date)])))

```

```{r}
Mean_Fluro_Time <- Data %>%
  group_by(Site) %>%
  summarise(Mean_Fluoro_Time = mean(Fluoroscopy_Time, na.rm = TRUE))

ggplot(Mean_Fluro_Time, aes(x = Site, y = Mean_Fluoro_Time)) +
  geom_col( fill = "steelblue", color = "black") +
  labs(title = "Mean Fluoroscopy Times by Site",
       x = "Site",
       y = "Mean Fluoroscopy Time (minutes)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
If we're looking at the data from the most broad viewpoint, we see that
Wilmington had the lowest Fluoro times averaged out over the study duration, 
with St. Louis, having the highest. Though it has yet to be determined whether 
these differences are significant. Despite this, it would be much more 
beneficial to look at the data as a progression rather than a blanket average 
as a whole.

```{r}
Monthly_Site_Averages <- Data %>%
    group_by(Site, Month) %>%
    summarise(Mean_Fluoroscopy_Time = mean(Fluoroscopy_Time, na.rm = TRUE), 
              .groups = "drop")
```

Let's look at each location individually as a time series progression.

Louisville
```{r}
Louisville <- Data %>% dplyr::filter (Site == "Louisville") %>% 
  arrange(Procedure_Date)

Plot1 <- ggplot(Louisville, aes(Procedure_Date, Fluoroscopy_Time)) + 
  geom_line(color = "steelblue") + 
geom_smooth(method = "loess", se = FALSE, color = "red", size=1) +
labs(x="Months", y="Fluoro Time", title= "Time Series of Louisville Fluro Time")

Louisville.Table <- tibble(
Month = c("August 2024", "September 2024", "October 2024", "November 2024", 
          "December 2024", "January 2025"),
Mean_Fluoroscopy_Time = c("28.60000", "32.90588", "30.99608", "25.27727", 
                          "27.01707", "27.28810")
)

Table <- ggtexttable(Louisville.Table, rows = NULL,
                  theme = ttheme("light"))
Plot1 / Table
```
Looking at the time series, it's difficult to infer any real difference in
fluoro time over the year. We'd expect a provider's performance to increase 
(inversely decreasing procedure time) over
the course of the year, but there seems to be small, most likely arbitrary 
differences in mean fluoroscopy time at the Louisville site. However, 
it is worth a look to see if any of the differences are statistically 
significant. 

```{r}
Louisville$Month <- factor(Louisville$Month)
Louisville.Anova <- aov(Fluoroscopy_Time ~ Month, data = Louisville)
summary(Louisville.Anova)

TukeyHSD(Louisville.Anova)

effectsize(Louisville.Anova)

```
First off, a one-way ANOVA test of the two variables was performed 
(month and fluoro time). The test returned a significant result 
(F(5, 218) = 3.877, p < 000219)) so there appears to be some significant 
difference between at least two of the months based on average fluoro time. 

To properly identify the months in which there was a significant difference, 
the TukeyHSD post-hoc test was performed. This found a significant difference 
between October 2024 and November 2024, as well as September 2024 and 
November 2024. These p-values were 0.02 and 0.003 respectively (p < 0.05). 
No other month-to-month comparisons, including between mid-2024 and 
January 2025, reached statistical significance. This is notable because one 
might expect the greatest difference during this later period, potentially 
reflecting increased cumulative treatment volume or enhanced training. 

Lastly, an effect size (Eta-squared) was caluclated, which came out to 0.08, 
meaning 8% of the variation in fluoroscopy time can be explained by the month 
in which the procedure was performed. Conversely, 92% of the variation is due to 
variability in the month itself, which tells us other variables may be more of a 
factor (procedure volume, average age of the patient, systemic disease, general 
anatomy, etc.). It figures that the inherent anatomical variance of patients 
could vary significantly within a month, causing the bulk of the variation. 
So while there did appear to be a significant difference between the months 
(only Oct./Nov. 2024 an Sep./Nov. 2024) in terms of fluoroscopy time, only a 
small portion of the variance is attributed to the data between the months, 
but rather than within. That being said, 8% could be of significance in regards 
to physician performance given the correct clinical context.


Arizona Site
```{r}
Arizona <- Data %>% dplyr::filter (Site == "Arizona") %>% 
  arrange(Procedure_Date)

Plot2 <- ggplot(Arizona, aes(Procedure_Date, Fluoroscopy_Time)) + 
  geom_line(color = "red") + 
geom_smooth(method = "loess", se = FALSE, color = "black", size=1) + labs(x="Months", y="Fluoro Time", title= "Time Series of Arizona Fluro Time")

Arizona.Table <- tibble(
Month = c("October 2023", "November 2023", "December 2023", "January 2024", 
          "February 2024", "March 2024", "April 2024", "May 2024", "June 2024", 
          "July 2024", "August 2024", "September 2024"),
Mean_Fluoroscopy_Time = c("33.2", "31.7", "30.4", "26.6", "29.3", "31.1", 
                          "28.2", "26.3", "26.7", "27.8", "29.1", "30.0")
)

Table2 <- ggtexttable(Arizona.Table, rows = NULL,
                  theme = ttheme("light", base_size=11))
Plot2
Table2
```
For Arizona, the time series shows a relatively straight trend line as well. The monthly averages are listed. We will test again for significace.

```{r}

Arizona$Month <- factor(Arizona$Month)
Arizona.Anova <- aov(Fluoroscopy_Time ~ Month, data = Arizona)
summary(Arizona.Anova)

TukeyHSD(Arizona.Anova)

effectsize(Arizona.Anova)

```
Another one-way ANOVA test of the two variables was performed. We have a 
p-value of 0.101 (p < 0.05) indicating no significant difference between the 
fluoro time between months over the year. 

This was confirmed with the post-hoc test showing no significant difference 
between any monthly pairwise comparisons. 

The effect size was calculated at 3% which is not statistically relevent in 
terms of explaining the variation of fluoroscopy time over the months. 
3% is too small to be clinically relevent. In summary, Arizona did not show any 
meaningful difference in fluoroscopy time over the year of data analyzed. 

St. Louis
```{r}

Data <- Data %>%
  mutate(Site = recode(Site, `St. Louis` = "St.Louis"))

St.Louis <- Data %>% dplyr::filter (Site == "St.Louis") %>% 
  arrange(Procedure_Date)

Plot3 <- ggplot(St.Louis, aes(Procedure_Date, Fluoroscopy_Time)) + 
  geom_line(color = "blue") + 
geom_smooth(method = "loess", se = FALSE, color = "orange", size=1) +
labs(x="Months", y="Fluoro Time", title= "Time Series of St.Louis Fluro Time")

St.Louis.Table <- tibble(
Month = c("July 2023", "August 2023", "September 2023", "October 2023", 
          "November 2023", "December 2023", "January 2024", "February 2024", 
          "March 2024", "April 2024", "May 2024", "June 2024",
"July 2024", "August 2024", "September 2024", "October 2024", "November 2024", 
"December 2024",
  "January 2025", "February 2025"),
  Mean_Fluoroscopy_Time = c(14.4, 36.7, 35.1, 45.6, 32.1, 33.1,
                            32.8, 37.0, 47.8, 34.8, 43.3, 30.3,
                            29.2, 29.7, 32.0, 27.4, 30.4, 41.3,
                            31.7, 31.3)
)

Table3 <- ggtexttable(St.Louis.Table, rows = NULL,
                  theme = ttheme("light", base_size=6))
Plot3
Table3

```

```{r}
St.Louis$Month <- factor(St.Louis$Month)
St.Louis.Anova <- aov(Fluoroscopy_Time ~ Month, data = St.Louis)

summary(St.Louis.Anova)


TukeyHSD(St.Louis.Anova)

effectsize(St.Louis.Anova)

```
For St. Louis, the ANOVA returned a significant effect of month on fluoroscpy 
time (p= 0.001440, p < 0.05). However, the post-hoc test 
(again using Tukey's HSD) revealed no significant pairwise interactions between 
the individual months, and the effect size remains extremely low (0.04). It 
would be hard to attribute any change in fluoroscopy time to monthly 
performance, and to that affect, the monthly change in performance of the 
provider.

Taken together, the ANOVA indicated some statistically significant effect of 
month on fluoroscopy time, but the abscence of any signifcant pairwise 
comparisons, and small effect size indicate that the data is practically 
meaninful. It would not be appropriate to attribute the differences to physician 
improvement. 

Syracuse/AMP

```{r}

Data <- Data[-c(2089, 1865, 1946), ]

Data <- Data %>%
mutate(Site = recode(Site, `Syracuse/AMP` = "Syracuse"))


Syracuse <- Data %>% dplyr::filter (Site == "Syracuse") %>% 
  arrange(Procedure_Date)

Plot4 <- ggplot(Syracuse, aes(Procedure_Date, Fluoroscopy_Time)) + 
  geom_line(color = "black") + 
geom_smooth(method = "loess", se = FALSE, color = "purple", size=1) +
labs(x="Months", y="Fluoro Time", 
     title= "Time Series of Syracuse/AMP Fluro Time")

Syracuse.Table <- tibble( 
Month = c("July 2024","August 2024","September 2024","October 2024", 
          "November 2024", "December 2024", "January 2025", "February 2025"),
Mean_Fluoroscopy_Time = c(32.1, 35.1, 33.5, 26.9, 29.2, 28.4, 22.2, 23.0
  ))


Table4 <- ggtexttable(Syracuse.Table, rows = NULL,
                  theme = ttheme("light", base_size=11))
Plot4
Table4

Syracuse_counts <- Data %>%
filter(Site == "Syracuse") %>%
mutate(Month = format(Procedure_Date, "%B %Y")) %>%
group_by(Month) %>%
summarise(Count = n()) %>%
arrange(as.Date(paste0("01 ", Month), "%d %B %Y"))
Syracuse_counts

```
Interestingly enough the trend line for Syracuse does appear to be decreasing in 
a meaningful way. There is only 2 cases for July of 2024, but there is > 28 for 
all other months which satisfies the appropriate case volume when generating 
the monthly averages. 

```{r}
Syracuse$Month <- factor(Syracuse$Month)
Syracuse.Anova <- aov(Fluoroscopy_Time ~ Month, data = Syracuse)
summary(Syracuse.Anova)


effectsize(Syracuse.Anova)

Tukey <- TukeyHSD(Syracuse.Anova)
tukey_month <- Tukey$Month
signif_rows <- tukey_month[tukey_month[, "p adj"] < 0.05, ]
print(signif_rows)


```
As expected, the ANOVA test returned a very low p-value of 5.1e^-10 
(p < 0.05, 95% CI), confirming that there is a significant change in average 
fluoroscopy time over the course of the given time frame. Given the extensive 
list of pairwise comparisons, they were condensed to show the months in which 
there is significant pairwise interaction. While there is some significant 
month to month variation, it's important to note that there is also significant
variation across January/February 2025 and August 2024. This allows the 
inference that the provider significantly changed his average fluoroscopy time
over the entire time frame. The effect size of 18% indicates that the month of 
the procedure explains about 18% of the variability in fluoroscopy time. 
This suggests a moderate effect, likely reflecting the provider's improvement 
over time. However, this (and all prior) analysis considers only the passage 
of time (months) and does not account for other potential factors that might 
also influence fluoroscopy time, which in the scope of interventional radiolgy,
can be quite large. 

In summary, the 18% effect size reflects how much of the variability in 
fluoroscopy time is explained by time progression (months). Skill improvement is 
probably a major contributor to this, but the effect also includes all other 
time-related changes.

Wilmington

```{r}

Wilmington <- Data %>% dplyr::filter (Site == "Wilmington") %>% 
  arrange(Procedure_Date)

Plot5 <- ggplot(Wilmington, aes(Procedure_Date, Fluoroscopy_Time)) + 
  geom_line(color = "green") + 
geom_smooth(method = "loess", se = FALSE, color = "red", size=1) +
labs(x="Months", y="Fluoro Time", title= "Time Series of Wilmington Fluro Time")

Wilmington.Table <- tibble( 
Month = c("June 2024", "July 2024", "August 2024", "September 2024", 
          "October 2024", "November 2024", "December 2024", "January 2025", 
          "February 2025"
),
Mean_Fluoroscopy_Time = c(
    16.4, 31.8, 34.0, 32.8, 
    25.2, 26.1, 24.1, 
    22.2, 22.8
))


Table5 <- ggtexttable(Wilmington.Table, rows = NULL,
                  theme = ttheme("light", base_size=11))
Plot5
Table5

Wilmington_counts <- Data %>%
filter(Site == "Wilmington") %>%
mutate(Month = format(Procedure_Date, "%B %Y")) %>%
group_by(Month) %>%
summarise(Count = n()) %>%
arrange(as.Date(paste0("01 ", Month), "%d %B %Y"))
Wilmington_counts

```

```{r}

Wilmington$Month <- factor(Wilmington$Month)
Wilmington.Anova <- aov(Fluoroscopy_Time ~ Month, data = Wilmington)
summary(Wilmington.Anova)

effectsize(Wilmington.Anova)

Tukey1 <- TukeyHSD(Wilmington.Anova)
tukey_month1 <- Tukey1$Month
signif_rows1 <- tukey_month1[tukey_month1[, "p adj"] < 0.05, ]
print(signif_rows1)

```

The ANOVA for Wilmington returned a p-value of 1.88e^08, showing high 
significance in fluoro time differences between the months (p < 0.05, 95% CI). 
The effect size was 17%, similar to Syracuse. See the explanation under the 
Syracuse analysis, as it would be practically identical to what would be written here. There again was a significant difference between the earliest month and the last months of the data set

CROSS SITE ANALYSIS

Generalized Addative Model

Now that each site has been analyzed individually, the next step is to evaluate 
which training method performs best across all clinical sites collectively. 
To analyze the variation in fluoroscopy time over several months across multiple 
sites, I chose to use a Generalized Additive Model (GAM) with Site included as 
a factor variable.

This modeling approach offers the flexibility to capture nonlinear trends in 
fluoroscopy time over time within each site, while explicitly accounting for 
differences between sites as categorical groups. Treating Site as a factor 
ensures the model recognizes each location as a distinct entity and estimates 
unique smooth temporal patterns for each site, rather than assuming a uniform or 
numeric relationship across all sites.

This flexibility is important because each site may have different training 
methods, workflows, or operational practices that produce distinct temporal 
dynamics in fluoroscopy times. By including site-specific smooth terms, the GAM 
can more accurately model these complex patterns, enabling a deeper 
understanding of how fluoroscopy efficiency evolves differently across locations 
and, ultimately, how the various training methods compare.

```{r}
Data1 <- Data %>%
  mutate(Month_Date = my(Month)) %>%
  group_by(Site) %>%
  arrange(Site, Month_Date) %>%
  mutate(Month_Num = dense_rank(Month_Date)) %>%
  ungroup()

Data1$Site <- as.factor(Data1$Site)

gam_model <- gam(Fluoroscopy_Time ~ Site + s(Month_Num, by = Site), 
                 data = Data1)

summary(gam_model)
plot(gam_model, pages = 1)
gam.check(gam_model)
```


The parametric coefficients indicate significant baseline differences in 
average fluoroscopy time between sites. Specifically, compared to the reference 
site (Arizona), Louisville and Syracuse had significantly lower baseline 
fluoroscopy times (approximately 5.7 and 7 units lower, respectively; p < 0.05), 
while St. Louis had a significantly higher baseline time (+4 units, p < 0.001). 
Wilmington did not differ significantly from Arizona in baseline fluoroscopy 
time.

The smooth terms for month within each site revealed significant nonlinear 
temporal patterns for most sites. St. Louis, Syracuse, and Wilmington exhibited 
complex and highly significant nonlinear trends (effective degrees of
freedom > 4, p < 0.001), indicating that fluoroscopy times changed in a 
non-monotonic way across months. Louisville’s temporal trend was simpler but 
still significant (edf = 1, p = 0.028), while Arizona’s trend was marginally 
nonsignificant (p = 0.056). These findings suggest that fluoroscopy time 
performance evolved differently over time at each site, with some sites showing 
periods of improvement or fluctuation not captured by simple linear trends.

Overall, this model demonstrates meaningful differences in fluoroscopy time 
between sites and reveals distinct temporal trajectories within each site. 
This supports the hypothesis that site-specific factors, such as training 
methods and operational practices, influence the evolution of fluoroscopy 
efficiency over time. The GAM’s flexibility in capturing nonlinear time effects
provides a nuanced understanding that simpler linear models would miss.


```{r}
new_data <- Data1 %>%
  select(Site, Month_Num) %>%
  distinct() %>%
  arrange(Site, Month_Num)

new_data <- new_data %>%
  mutate(pred = predict(gam_model, newdata = ., se.fit = TRUE)$fit,
         se = predict(gam_model, newdata = ., se.fit = TRUE)$se.fit,
         lower = pred - 2 * se,
         upper = pred + 2 * se)


ggplot(new_data, aes(x = Month_Num, y = pred, color = Site, fill = Site)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, color = NA) +
  labs(
    title = "GAM-Fitted Trends in Fluoroscopy Time by Site",
    x = "Month Number (relative time)",
    y = "Predicted Fluoroscopy Time (minutes)"
  ) +
  theme_minimal(base_size = 14) +
  theme(legend.position = "bottom")


```
The figure displays site-specific temporal trends in fluoroscopy time as modeled 
by the GAM. Solid lines represent the predicted mean fluoroscopy time across 
months for each site, while the shaded ribbons indicate approximate 95% 
confidence intervals around these predictions. The varying shapes of the curves 
highlight differences in how fluoroscopy time evolved over time at each clinical 
site. Sites with more pronounced curves and wider ribbons reflect greater 
nonlinear changes and uncertainty in the trend, consistent with the GAM results. 
This visualization complements the statistical findings by illustrating the 
unique temporal patterns captured by the model.
```{r}

derivs <- derivatives(gam_model)


derivs_filtered <- derivs %>%
  filter(grepl("Month_Num", .smooth))

derivs_summary <- derivs_filtered %>%
  group_by(Site) %>%
  summarise(
    Avg_Derivative = mean(`.derivative`),
    Min_Derivative = min(`.derivative`),
    Max_Derivative = max(`.derivative`)
  ) %>%
  arrange(Avg_Derivative)

# Print summary
print(derivs_summary)

ggplot(derivs_summary, aes(x = reorder(Site, Avg_Derivative), 
                           y = Avg_Derivative)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(title = "Average Monthly Rate of Change in Fluoroscopy Time by Site",
       x = "Site",
       y = "Average Derivative (minutes per month)") +
  theme_minimal()
```

To better understand how fluoroscopy time is evolving over the study period at
each clinical site, the first derivatives of the smooth terms from the GAM model 
were computed. These derivatives represent the instantaneous rate of change in 
fluoroscopy time with respect to month number. Negative derivative values 
indicate a decrease in fluoroscopy time (improvement), while positive values 
indicate an increase (worsening).

The derivatives were summarized by site, calculating the average rate of change 
as well as the minimum and maximum observed rates during the study period. 
This summary provides insight into both the overall trend and the variability 
of change over time for each site.

Louisville and Syracuse show a negative average derivative indicating 
improvement in fluoroscopy time over time

Arizona and St. Louis show a relatively neutral average derivative over time 
indicating flucating or stable performance

Wilmington showed an average derivative increase over time, concluding that the 
fluoroscopy time actually worsened as the time period went on 

The accompanying bar plot visualizes these average rates of change for each 
site, with error bars representing the range of observed rates. This allows 
for quick comparison of performance dynamics across sites and highlights those 
with the most favorable or concerning trends.

Overall, this derivative analysis complements the GAM-fitted trends by 
quantifying the speed and direction of change, helping to identify which sites 
are improving fluoroscopy efficiency most rapidly, which are stable, and which 
may need further investigation.
```{r}

derivs_summary <- derivs %>%
  group_by(Site) %>%
  summarise(
    Avg_Derivative = mean(.derivative),
    Min_Derivative = min(.derivative),
    Max_Derivative = max(.derivative),
    Lower_CI = mean(.lower_ci),
    Upper_CI = mean(.upper_ci),
    .groups = "drop"
  )

ggplot(derivs_summary, aes(x = reorder(Site, Avg_Derivative), 
                           y = Avg_Derivative)) +
  geom_col(fill = "steelblue") +
  geom_errorbar(aes(ymin = Lower_CI, ymax = Upper_CI), width = 0.3) +
  coord_flip() +
  labs(title = "Average Monthly Rate of Change in Fluoroscopy Time by 
       Site with 95% CI",
       x = "Site",
       y = "Average Derivative (minutes per month)") +
  theme_minimal()
```
The bar plot displays the average monthly rate of change for each site, with 
error bars representing the 95% confidence intervals. Sites with confidence 
intervals entirely below zero suggest statistically significant decreases in 
fluoroscopy time, indicating consistent improvements. Conversely, sites with 
confidence intervals overlapping zero suggest less certain or more variable 
trends.

This analysis offers a clear comparative view of how fluoroscopy efficiency 
evolves across sites, highlighting those with robust improvements and others 
where changes may be less definitive. Such insights can guide targeted quality 
improvement efforts tailored to each site’s unique performance trajectory.

The confidence interval for the average monthly rate of change in fluoroscopy 
time at the Wilmington site is notably wide, indicating substantial uncertainty 
in the estimated trend. This high variability likely reflects limited or highly 
variable data for Wilmington, which reduces confidence in concluding whether 
fluoroscopy time is increasing or decreasing at this location. As a result, 
the trend estimates for Wilmington should be interpreted with caution, and 
further data collection or additional analysis may be necessary to clarify the 
true temporal pattern at this site.

```{r}

max_month_num <- max(Data1$Month_Num)
sites <- levels(Data1$Site)

future_months <- data.frame(
  Month_Num = rep((max_month_num + 1):(max_month_num + 6), 
                  times = length(sites)),
  Site = rep(sites, each = 6)
)

predictions <- predict(gam_model, newdata = future_months, se.fit = TRUE)

future_months <- future_months %>%
  mutate(
    Fluoroscopy_Time_Pred = predictions$fit,
    SE = predictions$se.fit,
    Lower_CI = Fluoroscopy_Time_Pred - 1.96 * SE,
    Upper_CI = Fluoroscopy_Time_Pred + 1.96 * SE
  )

start_date <- min(Data1$Month_Date)
future_months <- future_months %>%
  mutate(
    Forecast_Month = start_date %m+% months(Month_Num - 1)
  )


ggplot() +
  geom_point(data = Data1, aes(x = Month_Date, y = Fluoroscopy_Time, 
                               color = Site)) +
  geom_line(data = Data1, aes(x = Month_Date, y = Fluoroscopy_Time, 
                              color = Site)) +
  geom_line(data = future_months, aes(x = Forecast_Month, 
              y = Fluoroscopy_Time_Pred, color = Site), linetype = "dashed") +
  geom_ribbon(
    data = future_months,
    aes(x = Forecast_Month, ymin = Lower_CI, ymax = Upper_CI, 
        fill = Site, group = Site),
    alpha = 0.2,
    color = NA
  ) +
  labs(
    title = "Fluoroscopy Time: Observed and 6-Month Forecast",
    x = "Date",
    y = "Fluoroscopy Time"
  ) +
  theme_minimal()

```
Using the fitted Generalized Additive Model (GAM), fluoroscopy time trends for 
each clinical site six months beyond the observed data. The model provides 
predicted fluoroscopy times along with 95% confidence intervals to reflect 
uncertainty in these forecasts. These predictions, visualized as dashed lines 
with shaded confidence bands, extend the temporal patterns captured by the model 
and allow us to anticipate potential changes in fluoroscopy time over the near 
future. Such forecasting can guide ongoing evaluation of site performance and 
training effectiveness, while highlighting where further monitoring or 
intervention might be needed.

